---
title: "Untitled"
author: "slinkly linc"
date: "11/8/2018"
output: html_document
---

```{r}
library(tidyverse) # dont think i need, actually
library(stringr)
```

```{r}
setwd('/Users/lincoln.harris/code/SNP_calling_pipeline/lolliplots/')
```

read in AA out
```{r}
egfr_df <- read.csv('/Users/lincoln.harris/code/SNP_calling_pipeline/py_notebooks/out/egfr_hits_AA.csv', header = F)
kras_df <- read.csv('/Users/lincoln.harris/code/SNP_calling_pipeline/py_notebooks/out/kras_hits_AA.csv', header = F)
braf_df <- read.csv('/Users/lincoln.harris/code/SNP_calling_pipeline/py_notebooks/out/braf_hits_AA.csv', header = F)
```

get rid of special characters
```{r}
egfr_df$V2 <- gsub('[[]]', '', egfr_df$V2)
egfr_df$V2 <- gsub('[[]', '', egfr_df$V2)
egfr_df$V2 <- gsub('[]]', '', egfr_df$V2)
egfr_df$V2 <- gsub("'", '', egfr_df$V2)

kras_df$V2 <- gsub('[[]]', '', kras_df$V2)
kras_df$V2 <- gsub('[[]', '', kras_df$V2)
kras_df$V2 <- gsub('[]]', '', kras_df$V2)
kras_df$V2 <- gsub("'", '', kras_df$V2)

braf_df$V2 <- gsub('[[]]', '', braf_df$V2)
braf_df$V2 <- gsub('[[]', '', braf_df$V2)
braf_df$V2 <- gsub('[]]', '', braf_df$V2)
braf_df$V2 <- gsub("'", '', braf_df$V2)
```

split AA cols based on ','
```{r}
toAdd_egfr <- str_split_fixed(egfr_df$V2, ",", 10)
toAdd_kras <- str_split_fixed(kras_df$V2, ",", 10)
toAdd_braf <- str_split_fixed(braf_df$V2, ",", 10)
```

add separate col for each AA entry
```{r}
# how many to add? -- there has to be a smarter way of doing this
egfr_df$V2 <- toAdd_egfr[,1]
egfr_df$V3 <- toAdd_egfr[,2]
egfr_df$V4 <- toAdd_egfr[,3]
egfr_df$V5 <- toAdd_egfr[,4]
egfr_df$V6 <- toAdd_egfr[,5]
egfr_df$V7 <- toAdd_egfr[,6]
egfr_df$V8 <- toAdd_egfr[,7]
egfr_df$V9 <- toAdd_egfr[,8]
egfr_df$V10 <- toAdd_egfr[,9]

kras_df$V2 <- toAdd_kras[,1] # definetly dont need 10 here
kras_df$V3 <- toAdd_kras[,2]
kras_df$V4 <- toAdd_kras[,3]
kras_df$V5 <- toAdd_kras[,4]
kras_df$V6 <- toAdd_kras[,5]
kras_df$V7 <- toAdd_kras[,6]
kras_df$V8 <- toAdd_kras[,7]
kras_df$V9 <- toAdd_kras[,8]
kras_df$V10 <- toAdd_kras[,9]

braf_df$V2 <- toAdd_braf[,1] # or here
braf_df$V3 <- toAdd_braf[,2]
braf_df$V4 <- toAdd_braf[,3]
braf_df$V5 <- toAdd_braf[,4]
braf_df$V6 <- toAdd_braf[,5]
braf_df$V7 <- toAdd_braf[,6]
braf_df$V8 <- toAdd_braf[,7]
braf_df$V9 <- toAdd_braf[,8]
braf_df$V10 <- toAdd_braf[,9]
```

replace blanks with NA
```{r}
egfr_df[ egfr_df == "" ] = NA
kras_df[ kras_df == "" ] = NA
braf_df[ braf_df == "" ] = NA
```

remove empty rows and cols
```{r}
egfr_df <- egfr_df[,colSums(is.na(egfr_df)) != nrow(egfr_df)] # remove cols
kras_df <- kras_df[,colSums(is.na(kras_df)) != nrow(kras_df)] # remove cols
braf_df <- braf_df[,colSums(is.na(braf_df)) != nrow(braf_df)] # remove cols
```

get rid of cell names col
```{r}
row.names(egfr_df) <- egfr_df[,1]
egfr_df <- egfr_df[,-1]

row.names(kras_df) <- kras_df[,1]
kras_df <- kras_df[,-1]

row.names(braf_df) <- braf_df[,1]
braf_df$V1 <- NULL
```

set colnames
```{r}
egfr_cols <- c('EGFRmut1', 'EGFRmut2', 'EGFRmut3', 'EGFRmut4', 'EGFRmut5', 'EGFRmut6')
colnames(egfr_df) <- egfr_cols

kras_cols <- c('KRASmut1', 'KRASmut2')
colnames(kras_df) <- kras_cols

braf_cols <- c('BRAFmut1')
colnames(braf_df) <- braf_cols
```

what if i wanted to add all 3 of these bastards to one big ass table? 
  hell yeah!!
```{r}
big_df <- merge(egfr_df, kras_df, by="row.names")
row.names(big_df) <- big_df[,1]
big_df$Row.names <- NULL

big_df <- merge(big_df, braf_df, by="row.names")
row.names(big_df) <- big_df[,1]
big_df$Row.names <- NULL
```

ADD RAW COUNTS INFO

read in new csvs
```{r}
braf_counts_df <- read.csv('/Users/lincoln.harris/code/SNP_calling_pipeline/py_notebooks/out/braf_hits.csv', header = F)
egfr_counts_df <- read.csv('/Users/lincoln.harris/code/SNP_calling_pipeline/py_notebooks/out/egfr_hits.csv', header = F)
kras_counts_df <- read.csv('/Users/lincoln.harris/code/SNP_calling_pipeline/py_notebooks/out/kras_hits.csv', header = F)
```

set rownames for these guys
```{r}
row.names(braf_counts_df) <- braf_counts_df[,1]
row.names(kras_counts_df) <- kras_counts_df[,1]
row.names(egfr_counts_df) <- egfr_counts_df[,1]
```

remove cell name cols
```{r}
braf_counts_df$V1 <- NULL
kras_counts_df$V1 <- NULL
egfr_counts_df$V1 <- NULL
```

set colnames for these guys
```{r}
colnames(braf_counts_df) <- 'BRAF_raw_counts'
colnames(kras_counts_df) <- 'KRAS_raw_counts'
colnames(egfr_counts_df) <- 'EGFR_raw_counts'
```

merge!!
```{r}
big_df <- merge(big_df, braf_counts_df, by='row.names')
row.names(big_df) <- big_df[,1] # why am i still doing this
big_df$Row.names <- NULL

big_df <- merge(big_df, kras_counts_df, by='row.names')
row.names(big_df) <- big_df[,1] # why am i still doing this
big_df$Row.names <- NULL

big_df <- merge(big_df, egfr_counts_df, by='row.names')
row.names(big_df) <- big_df[,1] # why am i still doing this
big_df$Row.names <- NULL
```

reorder
```{r}
big_df <- big_df[,c(10,12,11,9,1,2,3,4,5,6,7,8)]
```

/////////////////////////////////////////////////////////////////////
/////////////////////////////////////////////////////////////////////
/////////////////////////////////////////////////////////////////////

ADD PATIENT METADATA

read in per plate metadata
```{r}
metadata <- read.csv('/Users/lincoln.harris/Desktop/cDNA_plate_metadata.csv', header = T)
```

copy this guy 
```{r}
big_df1 <- big_df
```

add some new cols
```{r}
big_df1$plate <- NA
big_df1$patient_id <- NA
```

get plate name
```{r}
cells <- row.names(big_df1)
cells_splt <- strsplit(cells, '_')
cells_splt[[5]][2]
```

FINE ill do a for loop -- fill in PLATE vals
```{r}
for(i in 1:nrow(big_df1)){
  big_df1$plate[i] <- cells_splt[[i]][2]
}
```

maybe i need to do this? 
```{r}
big_df1$patient_id <- as.character(big_df1$patient_id)
```

another loop -- fill in PATIENT vals
```{r}
for(i in 1:nrow(big_df1)){
  currPlate <- big_df1$plate[i]
  matchingPatient_index <- which(metadata$plate == currPlate)
  matchingPatient_ID <- metadata$patient_id[matchingPatient_index]
  big_df1$patient_id[i] <- as.character(matchingPatient_ID)
}
```

lets reorder again 
  looks pretty good!
```{r}
big_df1 <- big_df1[,c(13,14,1,2,3,4,5,6,7,8,9,10,11,12)]
```

write 
```{r}
#write.csv(big_df1, 'completeMutationsDataframe.csv', row.names = T, quote = FALSE)
```

/////////////////////////////////////////////////////////////////////
/////////////////////////////////////////////////////////////////////
/////////////////////////////////////////////////////////////////////

GET MUTATIONS ON PER PATIENT BASIS

```{r}
unique(big_df1$patient_id)
```

```{r}
subset_i <- which(big_df1$patient_id == 'TH220')
subset <- big_df1[subset_i,]
head(subset)
```

get all reported mutations
```{r}
brafMuts <- subset$BRAFmut1

egfrMuts <- subset$EGFRmut1
egfrMuts <- c(egfrMuts, subset$EGFRmut2)
egfrMuts <- c(egfrMuts, subset$EGFRmut3)
egfrMuts <- c(egfrMuts, subset$EGFRmut4)
egfrMuts <- c(egfrMuts, subset$EGFRmut5)
egfrMuts <- c(egfrMuts, subset$EGFRmut6)

krasMuts <- subset$KRASmut1
krasMuts <- c(krasMuts, subset$KRASmut2)
```

get unique ones
```{r}
brafUnique <- unique(brafMuts)
egfrUnique <- unique(egfrMuts)
krasUnique <- unique(krasMuts)
```

remove NAs
```{r}
brafUnique <- brafUnique[!is.na(brafUnique)]
egfrUnique <- egfrUnique[!is.na(egfrUnique)]
krasUnique <- krasUnique[!is.na(krasUnique)]
```

money
```{r}
brafUnique
egfrUnique
krasUnique
```

set up new df to hold unique muts, for TH220
```{r}
patient_df <- data.frame(matrix(ncol = 3, nrow = 1))
row.names(patient_df) <- 'TH220'
colnames(patient_df) <- c('BRAF', 'EGFR', 'KRAS')
```

maybe i need to make these into vectors? 
```{r}
brafUnique <- as.vector(brafUnique)
egfrUnique <- as.vector(egfrUnique)
krasUnique <- as.vector(krasUnique)
```

fill in patient_df
```{r}
patient_df$BRAF <- list(brafUnique) 
patient_df$EGFR <- list(egfrUnique) 
patient_df$KRAS <- list(krasUnique) 
```

/////////////////////////////////////////////////////////////////////
/////////////////////////////////////////////////////////////////////
/////////////////////////////////////////////////////////////////////
