---
title: "scratch"
author: "slinkly linc"
date: "11/9/2018"
output: html_document
---

read in per plate metadata
```{r}
metadata <- read.csv('/Users/lincoln.harris/Desktop/cDNA_plate_metadata.csv', header = T)
```

copy this guy 
```{r}
big_df1 <- big_df
```

add some new cols
```{r}
big_df1$plate <- NA
big_df1$patient_id <- NA
```

get plate name
```{r}
cells <- row.names(big_df1)
cells_splt <- strsplit(cells, '_')
cells_splt[[5]][2]
```

FINE ill do a for loop -- fill in PLATE vals
```{r}
for(i in 1:nrow(big_df1)){
  big_df1$plate[i] <- cells_splt[[i]][2]
}
```

maybe i need to do this? 
```{r}
big_df1$patient_id <- as.character(big_df1$patient_id)
```

another loop -- fill in PATIENT vals
```{r}
for(i in 1:nrow(big_df1)){
  currPlate <- big_df1$plate[i]
  matchingPatient_index <- which(metadata$plate == currPlate)
  matchingPatient_ID <- metadata$patient_id[matchingPatient_index]
  big_df1$patient_id[i] <- as.character(matchingPatient_ID)
}
```

lets reorder again 
```{r}
big_df1 <- big_df1[,c(13,14,1,2,3,4,5,6,7,8,9,10,11,12)]
```

read in this more specific metadata file
```{r}
metadataAdv <- read.csv('/Users/lincoln.harris/Desktop/clinical_mt.csv', header = T)
```

/////////////////////////////////////////////////////////////////////
/////////////////////////////////////////////////////////////////////
/////////////////////////////////////////////////////////////////////
want to make a simple co-mutations table

```{r}
patientsList <- unique(cells_df$patient_id)
patientsList
```

not all of our patients made the final cut
```{r}
patientsList_rev <- c('TH067', 'TH158', 'TH223', 'TH266', 'TH103', 'TH169', 'TH199', 'TH225', 'TH107', 'TH171', 'TH205', 'TH226', 'TH146', 'TH172', 'TH208', 'TH227', 'TH150', 'TH174', 'TH210', 'TH231', 'TH179', 'TH217', 'TH236', 'TH155', 'TH218', 'TH238', 'TH156', 'TH183', 'TH220', 'TH157', 'TH185', 'TH222', 'TH248')
```

init new df
```{r}
coMut_df <- data.frame(matrix(ncol = 6, nrow = 33))
colNames_toAdd <- c('BRAF_mutations_raw', 'EGFR_mutations_raw', 'KRAS_mutations_raw', 'BRAF_mutations_norm', 'EGFR_mutations_norm', 'KRAS_mutations_norm')
colnames(coMut_df) <- colNames_toAdd
row.names(coMut_df) <- patientsList_rev
```

fill in coMut_df
  adding in normalization func
```{r}
for(i in 1:length(patientsList_rev)){
  currPatient <- patientsList_rev[i]
  currIndices <- which(cells_df$patient_id == currPatient)
  curr_df <- cells_df[currIndices,]
  numCells <- nrow(curr_df)

  brafHitCells <- which(curr_df$BRAF_raw_counts > 0)
  egfrHitCells <- which(curr_df$EGFR_raw_counts > 0)
  krasHitCells <- which(curr_df$KRAS_raw_counts > 0)

  coMut_df$BRAF_mutations_raw[i] <- length(brafHitCells)
  coMut_df$EGFR_mutations_raw[i] <- length(egfrHitCells)
  coMut_df$KRAS_mutations_raw[i] <- length(krasHitCells)
  
  brafHitsNorm <- length(brafHitCells) / numCells
  egfrHitsNorm <- length(egfrHitCells) / numCells
  krasHitsNorm <- length(krasHitCells) / numCells
  
  coMut_df$BRAF_mutations_norm[i] <- brafHitsNorm
  coMut_df$EGFR_mutations_norm[i] <- egfrHitsNorm
  coMut_df$KRAS_mutations_norm[i] <- krasHitsNorm
}
```

scale 
```{r}
coMut_df$BRAF_mutations_norm <- coMut_df$BRAF_mutations_norm * 1000
coMut_df$EGFR_mutations_norm <- coMut_df$EGFR_mutations_norm * 1000
coMut_df$KRAS_mutations_norm <- coMut_df$KRAS_mutations_norm * 1000
```

basic heatmap
```{r}
sub <- coMut_df[,c(4,5,6)]
data <- as.matrix(sub)
heatmap(data, scale = 'column')

# what if i do a log tranform
data <- log(data)
inf = which(data == '-Inf')
data[inf] <- 0
heatmap(data, scale = 'column', cexRow = 0.7, cexCol = 1.3)

```

pheatmap? 
```{r}
library(pheatmap)
#pdf('co-mutations_heatmap.pdf', 10, 10)
p <- pheatmap(data, cellheight = NA)
#dev.off()
```

/////////////////////////////////////////////////////////////////////
/////////////////////////////////////////////////////////////////////
/////////////////////////////////////////////////////////////////////
