---
title: "evaluateAgainstClustering"
author: "Lincoln"
date: "8/31/2018"
output: html_document

Want to take a look at bossman's Seurat object, and maybe take a look at where some of my cells map. 
  cant use the most recent one (July 30) bc it dosnt have a final_annotation metadata feature. 
  Instead gonna use the July 6th one. 
  
  Pulls from findDoubleMuts.Rmd
---

```{r}
load("/home/rstudio/15-lungAdeno_seurat/Seurat_objects_all_and_each_individual_LATESTcopy.RData")
```

```{r}
colnames(tiss_subset@meta.data)
```

```{r}
TSNEPlot(object = tiss_subset, do.label = T)
TSNEPlot(object = tiss_subset, do.label = T, group.by = 'final_annotation')
TSNEPlot(object = tiss_subset, do.label = T, group.by = 'patient_id')
TSNEPlot(object = tiss_subset, do.label = F, group.by = 'driver_gene')
```

get a list of EGFR mut cells to search for 
```{r}
egfrHit_cells <- gsub("_", ".", egfrHit_cells)
toSearch_indices <- which(row.names(tiss_subset@meta.data) %in% egfrHit_cells)
toSearch_cells <- row.names(tiss_subset@meta.data)[toSearch_indices]
```

artifically set the ident of EGFR mut cells 
```{r}
tiss_subset@ident[toSearch_indices] <- NA
```

where do they land on this plot? 
```{r}
pdf("tiss_subset_egfrHits.pdf", height = 10, width = 14)
TSNEPlot(object = tiss_subset, do.label = T)
dev.off()
```

///////////////////////////////////////////////////////////////////////////////
///////////////////////////////////////////////////////////////////////////////
///////////////////////////////////////////////////////////////////////////////

now lets do the same thing for KRAS
```{r}
krasHit_cells <- gsub("_", ".", krasHit_cells)
toSearch_indices <- which(row.names(tiss_subset@meta.data) %in% krasHit_cells)
toSearch_cells <- row.names(tiss_subset@meta.data)[toSearch_indices]
```

artifically set the ident of EGFR mut cells 
```{r}
tiss_subset@ident[toSearch_indices] <- NA
```

where do they land on this plot? 
```{r}
pdf("tiss_subset_krasHits.pdf", height = 10, width = 14)
TSNEPlot(object = tiss_subset, do.label = T)
dev.off()
```

///////////////////////////////////////////////////////////////////////////////
///////////////////////////////////////////////////////////////////////////////
///////////////////////////////////////////////////////////////////////////////

now P53
```{r}
p53Hit_cells <- gsub("_", ".", p53Hit_cells)
toSearch_indices <- which(row.names(tiss_subset@meta.data) %in% p53Hit_cells)
toSearch_cells <- row.names(tiss_subset@meta.data)[toSearch_indices]
```

artifically set the ident of EGFR mut cells 
```{r}
tiss_subset@ident[toSearch_indices] <- NA
```

where do they land on this plot? 
```{r}
pdf("tiss_subset_p53Hits.pdf", height = 10, width = 14)
TSNEPlot(object = tiss_subset, do.label = T)
dev.off()
```

///////////////////////////////////////////////////////////////////////////////
///////////////////////////////////////////////////////////////////////////////
///////////////////////////////////////////////////////////////////////////////

now lets look at Alk/Eml4 fusion cells
```{r}
# have to use periods here
alkFusCells <- c('C10.B003527', 'C15.B003527', 'I13.1001000369', 'J17.B003527', 'K11.B003588', 'M11.B003588', 'N14.B003588', 'O9.B000861')
toSearch_indices <- which(row.names(tiss_subset@meta.data) %in% alkFusCells)
```

what clusters do these guys land in? 
```{r}
tiss_subset@ident[toSearch_indices]
```

artifically set the ident of Alk/Eml4 fus cells
```{r}
tiss_subset@ident[toSearch_indices] <- NA
```

where do they land on this plot? 
```{r}
pdf("tiss_subset_alkFusHits.pdf", height = 10, width = 14)
TSNEPlot(object = tiss_subset, do.label = T)
dev.off()
```

///////////////////////////////////////////////////////////////////////////////
///////////////////////////////////////////////////////////////////////////////
///////////////////////////////////////////////////////////////////////////////

Get a list of all neoplastic cluster annotations
```{r}
unique(tiss_subset@meta.data$final_annotation)
tumorAnno <- c("Epithelial/tumor.TH249.P", "Epithelial/tumor.TH171.P", "Epithelial/tumor.TH179.P", "Epithelial/tumor.TH210.Ob", "Epithelial/tumor.TH231.P", "Epithelial/tumor.TH178.P", "Epithelial/tumor.TH248.P", "Epithelial/tumor.TH210.Oa", "Epithelial/tumor.TH227.P", "Epithelial/tumor.TH220.P", "Epithelial/tumor.TH107.Ob", "Epithelial/tumor.TH107.Oa", "Epithelial/tumor.TH067.P")
```

Define lists of neoplastic v. non-neoplastic cells
```{r}
neoCellIndicies <- which(tiss_subset@meta.data$final_annotation %in% tumorAnno)
neoCells <- row.names(tiss_subset@meta.data)[neoCellIndicies]
length(neoCells)

nonNeoCellIndicies <- which(!(tiss_subset@meta.data$final_annotation %in% tumorAnno))
nonNeoCells <- row.names(tiss_subset@meta.data)[nonNeoCellIndicies]
length(nonNeoCells)
```

get cell names for each cluster
```{r}
c0_indices <- which(tiss_subset@ident == 0)
c1_indices <- which(tiss_subset@ident == 1)
c2_indices <- which(tiss_subset@ident == 2)
c3_indices <- which(tiss_subset@ident == 3)
c4_indices <- which(tiss_subset@ident == 4)
c5_indices <- which(tiss_subset@ident == 5)
c6_indices <- which(tiss_subset@ident == 6)
c7_indices <- which(tiss_subset@ident == 7)
c8_indices <- which(tiss_subset@ident == 8)
c9_indices <- which(tiss_subset@ident == 9)
c10_indices <- which(tiss_subset@ident == 10)
c11_indices <- which(tiss_subset@ident == 11)
c12_indices <- which(tiss_subset@ident == 12)
c13_indices <- which(tiss_subset@ident == 13)
c14_indices <- which(tiss_subset@ident == 14)

c0_cells <- row.names(tiss_subset@meta.data)[c0_indices]
c1_cells <- row.names(tiss_subset@meta.data)[c1_indices]
c2_cells <- row.names(tiss_subset@meta.data)[c2_indices]
c3_cells <- row.names(tiss_subset@meta.data)[c3_indices]
c4_cells <- row.names(tiss_subset@meta.data)[c4_indices]
c5_cells <- row.names(tiss_subset@meta.data)[c5_indices]
c6_cells <- row.names(tiss_subset@meta.data)[c6_indices]
c7_cells <- row.names(tiss_subset@meta.data)[c7_indices]
c8_cells <- row.names(tiss_subset@meta.data)[c8_indices]
c9_cells <- row.names(tiss_subset@meta.data)[c9_indices]
c10_cells <- row.names(tiss_subset@meta.data)[c10_indices]
c11_cells <- row.names(tiss_subset@meta.data)[c11_indices]
c12_cells <- row.names(tiss_subset@meta.data)[c12_indices]
c13_cells <- row.names(tiss_subset@meta.data)[c13_indices]
c14_cells <- row.names(tiss_subset@meta.data)[c14_indices]
```

replace the periods
```{r}
c0_cells <- gsub("[.]", "_", c0_cells)
c1_cells <- gsub("[.]", "_", c1_cells)
c2_cells <- gsub("[.]", "_", c2_cells)
c3_cells <- gsub("[.]", "_", c3_cells)
c4_cells <- gsub("[.]", "_", c4_cells)
c5_cells <- gsub("[.]", "_", c5_cells)
c6_cells <- gsub("[.]", "_", c6_cells)
c7_cells <- gsub("[.]", "_", c7_cells)
c8_cells <- gsub("[.]", "_", c8_cells)
c9_cells <- gsub("[.]", "_", c9_cells)
c10_cells <- gsub("[.]", "_", c10_cells)
c11_cells <- gsub("[.]", "_", c11_cells)
c12_cells <- gsub("[.]", "_", c12_cells)
c13_cells <- gsub("[.]", "_", c13_cells)
c14_cells <- gsub("[.]", "_", c14_cells)
```

write csv
```{r}
write.table(c0_cells, "c0_cell_names.csv", row.names = F, quote = F, col.names = F)
write.table(c1_cells, "c1_cell_names.csv", row.names = F, quote = F, col.names = F)
write.table(c2_cells, "c2_cell_names.csv", row.names = F, quote = F, col.names = F)
write.table(c3_cells, "c3_cell_names.csv", row.names = F, quote = F, col.names = F)
write.table(c4_cells, "c4_cell_names.csv", row.names = F, quote = F, col.names = F)
write.table(c5_cells, "c5_cell_names.csv", row.names = F, quote = F, col.names = F)
write.table(c6_cells, "c6_cell_names.csv", row.names = F, quote = F, col.names = F)
write.table(c7_cells, "c7_cell_names.csv", row.names = F, quote = F, col.names = F)
write.table(c8_cells, "c8_cell_names.csv", row.names = F, quote = F, col.names = F)
write.table(c9_cells, "c9_cell_names.csv", row.names = F, quote = F, col.names = F)
write.table(c10_cells, "c10_cell_names.csv", row.names = F, quote = F, col.names = F)
write.table(c11_cells, "c11_cell_names.csv", row.names = F, quote = F, col.names = F)
write.table(c12_cells, "c12_cell_names.csv", row.names = F, quote = F, col.names = F)
write.table(c13_cells, "c13_cell_names.csv", row.names = F, quote = F, col.names = F)
write.table(c14_cells, "c14_cell_names.csv", row.names = F, quote = F, col.names = F)
```

///////////////////////////////////////////////////////////////////////////////
///////////////////////////////////////////////////////////////////////////////
///////////////////////////////////////////////////////////////////////////////

