---
title: "findHitsAndCrossValidate4"
author: "Lincoln"
date: "9/20/2018"
output: html_document

# Just want to count straight up mutations here, skipping COSMIC validation step
#   works
---

Define a function to read VCF files into neat dataframes
```{r}
readVCF_func <- function(currFile, fileName){
    vcf <- read.vcfR(currFile, verbose = F) # read file
    df <- as.data.frame(vcf@fix)
    numHits <- length(unique(df$POS))
    return(numHits)
}
```

MAIN function here
  Get a list of all the VCF files in a directory, pass these to our readVCF function, w/in a loop
```{r, error=F, warning=F}
files <- list.files(path="../02-epithelialVCF_all_out/", pattern="*.vcf", full.names=TRUE, recursive=FALSE)

outputDF <- data.frame(matrix(ncol = 2, nrow = 1)) # dataframe to store the output cellNames, plus metadata
outputDF_colnames <- c("cellName", "numHits")
colnames(outputDF) <- outputDF_colnames

for(i in 1:length(files)){
  f <- gsub("../02-epithelialVCF_all_out//", "", files[i])
  f1 <- gsub("_out.vcf", "", f) # parse file path to get cell name 
  hitsFound <- readVCF_func(files[i], f1)
  toAdd <- c(f1, hitsFound)
  outputDF[i,] <- toAdd
}
```

//////////////////////////////////////////////////////////////////////////
//////////////////////////////////////////////////////////////////////////
//////////////////////////////////////////////////////////////////////////

RUN SEURAT

Load libraries
```{r}
library(Seurat)
library(Matrix)
library(dplyr)
```

load object
```{r}
load("/home/rstudio/15-lungAdeno_seurat/Seurat_objects_all_and_each_individual_LATESTcopy.RData")
```

```{r}
colnames(tiss_subset@meta.data)
```

visualize
```{r}
TSNEPlot(object = tiss_subset, do.label = T)
TSNEPlot(object = tiss_subset, do.label = T, group.by = 'final_annotation')
TSNEPlot(object = tiss_subset, do.label = T, group.by = 'patient_id')
TSNEPlot(object = tiss_subset, do.label = F, group.by = 'driver_gene')
```

JUST NEOPLASTIC CELLS

remove TH041 -- ovary sample
```{r}
toRemove <- which(tiss_subset@meta.data$patient_id == 'TH041')
tiss_subset@ident[toRemove] <- 15

tiss_subset1 <- SubsetData(tiss_subset, ident.remove = NA, do.clean = F)
```

subset Seurat obj
  Neoplastic clusters are c(5,6,8,2,13,12,14)
```{r}
justMalig <- SubsetData(tiss_subset1, ident.use = c(5,6,8,2,13,12,14), do.clean = T)
```

Normalize and scale
```{r}
justMalig <- NormalizeData(object = justMalig)
justMalig <- ScaleData(object = justMalig)
```

Run PCA
```{r}
justMalig <- FindVariableGenes(object = justMalig, do.plot = TRUE, x.high.cutoff = Inf, y.cutoff = 0.5)
justMalig <- RunPCA(object = justMalig, do.print = FALSE)
justMalig <- ProjectPCA(object = justMalig, do.print = FALSE)
```

Elbow plot
```{r}
PCElbowPlot(object = justMalig)
```

Find Clusters
```{r}
justMalig <- FindClusters(object = justMalig, reduction.type = "pca", dims.use = 1:12, resolution = 0.5, print.output = 0, save.SNN = TRUE, force.recalc = TRUE)
```

run tSNE
```{r}
justMalig <- RunTSNE(object = justMalig, dims.use = 1:15, perplexity= 35)
```

visualize
```{r}           
pdf("blaa.pdf",15,10)
TSNEPlot(object = justMalig, do.label = T)
dev.off()

TSNEPlot(object = justMalig, do.label = T, group.by = 'patient_id')
TSNEPlot(object = justMalig, do.label = T, group.by = 'final_annotation')
```

//////////////////////////////////////////////////////////////////////////
//////////////////////////////////////////////////////////////////////////
//////////////////////////////////////////////////////////////////////////

replace underscore with period
```{r}
outputDF$cellName <- gsub("_", ".", outputDF$cellName)
```

sanity check
```{r}
which(row.names(justMalig@meta.data) %in% outputDF$cellName)
```

add a new col to metadata
```{r}
justMalig@meta.data$totalNumHits <- NA
```

and fill in -- think this worked
```{r}
for(i in 1:nrow(justMalig@meta.data)){
  if(row.names(justMalig@meta.data)[i] %in% outputDF$cellName){
    my_index <- which(outputDF$cellName == row.names(justMalig@meta.data)[i])
    nHits <- as.numeric(outputDF$numHits[my_index])
    justMalig@meta.data$totalNumHits[i] <- nHits
  }
}
```

set NAs to 0? 
```{r}
toZero <- which(is.na(justMalig@meta.data$totalNumHits))
justMalig@meta.data$totalNumHits[toZero] <- 0
```

plot
```{r}
#pdf("tst.pdf", 100, 10)
#TSNEPlot(object = justMalig, do.label = F, group.by = 'totalNumHits')
#dev.off()

#pdf("totalNumHits.pdf", 15, 10)
FeaturePlot(justMalig, features.plot = 'totalNumHits', cols.use = c('lightgrey', 'blue'), pt.size = 2)
#dev.off()
```

//////////////////////////////////////////////////////////////////////////
//////////////////////////////////////////////////////////////////////////
//////////////////////////////////////////////////////////////////////////

NMUTS, PER CLUSTER BASIS

can we make a barplot? 
```{r}
unique(justMalig@ident) # 12 clusters

c0_indices <- which(justMalig@ident == 0)
c0_cells <- row.names(justMalig@meta.data)[c0_indices]

c1_indices <- which(justMalig@ident == 1)
c1_cells <- row.names(justMalig@meta.data)[c1_indices]

c2_indices <- which(justMalig@ident == 2)
c2_cells <- row.names(justMalig@meta.data)[c2_indices]

c3_indices <- which(justMalig@ident == 3)
c3_cells <- row.names(justMalig@meta.data)[c3_indices]

c4_indices <- which(justMalig@ident == 4)
c4_cells <- row.names(justMalig@meta.data)[c4_indices]

c5_indices <- which(justMalig@ident == 5)
c5_cells <- row.names(justMalig@meta.data)[c5_indices]

c6_indices <- which(justMalig@ident == 6)
c6_cells <- row.names(justMalig@meta.data)[c6_indices]

c7_indices <- which(justMalig@ident == 7)
c7_cells <- row.names(justMalig@meta.data)[c7_indices]

c8_indices <- which(justMalig@ident == 8)
c8_cells <- row.names(justMalig@meta.data)[c8_indices]

c9_indices <- which(justMalig@ident == 9)
c9_cells <- row.names(justMalig@meta.data)[c9_indices]

c10_indices <- which(justMalig@ident == 10)
c10_cells <- row.names(justMalig@meta.data)[c10_indices]

c11_indices <- which(justMalig@ident == 11)
c11_cells <- row.names(justMalig@meta.data)[c11_indices]
```

get indicies
```{r}
outputDF_c0_indices <- which(outputDF$cellName %in% c0_cells)
outputDF_c1_indices <- which(outputDF$cellName %in% c1_cells)
outputDF_c2_indices <- which(outputDF$cellName %in% c2_cells)
outputDF_c3_indices <- which(outputDF$cellName %in% c3_cells)
outputDF_c4_indices <- which(outputDF$cellName %in% c4_cells)
outputDF_c5_indices <- which(outputDF$cellName %in% c5_cells)
outputDF_c6_indices <- which(outputDF$cellName %in% c6_cells)
outputDF_c7_indices <- which(outputDF$cellName %in% c7_cells)
outputDF_c8_indices <- which(outputDF$cellName %in% c8_cells)
outputDF_c9_indices <- which(outputDF$cellName %in% c9_cells)
outputDF_c10_indices <- which(outputDF$cellName %in% c10_cells)
outputDF_c11_indices <- which(outputDF$cellName %in% c11_cells)
```

fill in 
```{r}
outputDF$cluster <- NA

outputDF$cluster[outputDF_c0_indices] <- 0
outputDF$cluster[outputDF_c1_indices] <- 1
outputDF$cluster[outputDF_c2_indices] <- 2
outputDF$cluster[outputDF_c3_indices] <- 3
outputDF$cluster[outputDF_c4_indices] <- 4
outputDF$cluster[outputDF_c5_indices] <- 5
outputDF$cluster[outputDF_c6_indices] <- 6
outputDF$cluster[outputDF_c7_indices] <- 7
outputDF$cluster[outputDF_c8_indices] <- 8
outputDF$cluster[outputDF_c9_indices] <- 9
outputDF$cluster[outputDF_c10_indices] <- 10
outputDF$cluster[outputDF_c11_indices] <- 11
```

```{r}
outputDF$numHits <- as.numeric(outputDF$numHits)
p <- ggplot(outputDF, aes(x=cluster, y=numHits, group=cluster))
p + geom_boxplot() + scale_x_continuous(breaks = round(seq(min(outputDF$cluster), max(outputDF$cluster), by = 1)))
```

```{r}
tiss_subset_epi@meta.data$totalNumHits <- NA
```

and fill in -- think this worked
```{r}
for(i in 1:nrow(tiss_subset_epi@meta.data)){
  if(row.names(tiss_subset_epi@meta.data)[i] %in% outputDF$cellName){
    my_index <- which(outputDF$cellName == row.names(tiss_subset_epi@meta.data)[i])
    nHits <- as.numeric(outputDF$numHits[my_index])
    tiss_subset_epi@meta.data$totalNumHits[i] <- nHits
  }
}
```

set NAs to 0? 
```{r}
toZero <- which(is.na(tiss_subset_epi@meta.data$totalNumHits))
tiss_subset_epi@meta.data$totalNumHits[toZero] <- 0
```

export epi subset as pdf
```{r}
pdf("blaaa.pdf", 15, 10)
TSNEPlot(tiss_subset_epi, do.label = T)
dev.off()
```

plot epi subset, colored by mutations
```{r}
#pdf("totalNumHits_embed1.pdf", 15, 10)
FeaturePlot(tiss_subset_epi, features.plot = 'totalNumHits', cols.use = c('lightgrey', 'blue'), pt.size = 2, no.legend = F)  
#dev.off()
```