---
title: "subset_by_malig_and_map_hits_and_plot"
author: "Lincoln"
date: "9.15.2018"
output: html_document
---

Load libraries
```{r}
library(Seurat)
library(Matrix)
library(dplyr)
```

load object
```{r}
load("/home/rstudio/15-lungAdeno_seurat/Seurat_objects_all_and_each_individual_LATESTcopy.RData")
```

```{r}
colnames(tiss_subset@meta.data)
```

visualize
```{r}
TSNEPlot(object = tiss_subset, do.label = T)
TSNEPlot(object = tiss_subset, do.label = T, group.by = 'final_annotation')
TSNEPlot(object = tiss_subset, do.label = T, group.by = 'patient_id')
TSNEPlot(object = tiss_subset, do.label = F, group.by = 'driver_gene')
```

JUST NEOPLASTIC CELLS

remove TH041 -- ovary sample
```{r}
toRemove <- which(tiss_subset@meta.data$patient_id == 'TH041')
tiss_subset@ident[toRemove] <- 15

tiss_subset1 <- SubsetData(tiss_subset, ident.remove = NA, do.clean = F)
```

subset Seurat obj
  Neoplastic clusters are c(5,6,8,2,13,12,14)
```{r}
justMalig <- SubsetData(tiss_subset1, ident.use = c(5,6,8,2,13,12,14), do.clean = T)
```

Normalize and scale
```{r}
justMalig <- NormalizeData(object = justMalig)
justMalig <- ScaleData(object = justMalig)
```

Run PCA
```{r}
justMalig <- FindVariableGenes(object = justMalig, do.plot = TRUE, x.high.cutoff = Inf, y.cutoff = 0.5)
justMalig <- RunPCA(object = justMalig, do.print = FALSE)
justMalig <- ProjectPCA(object = justMalig, do.print = FALSE)
```

Elbow plot
```{r}
PCElbowPlot(object = justMalig)
```

Find Clusters
```{r}
justMalig <- FindClusters(object = justMalig, reduction.type = "pca", dims.use = 1:12, resolution = 0.5, print.output = 0, save.SNN = TRUE, force.recalc = TRUE)
```

run tSNE
```{r}
justMalig <- RunTSNE(object = justMalig, dims.use = 1:15, perplexity= 35)
```

visualize
```{r}                              
TSNEPlot(object = justMalig, do.label = T)
TSNEPlot(object = justMalig, do.label = T, group.by = 'patient_id')
TSNEPlot(object = justMalig, do.label = T, group.by = 'final_annotation')
```

get hits from GATK/COSMIC pipeline
```{r}
filtered_cosmic_hits_BRAF <- read.csv("filtered_cosmic_hits_BRAF.csv", header = T)
filtered_cosmic_hits_EGFR <- read.csv("filtered_cosmic_hits_EGFR.csv", header = T)
filtered_cosmic_hits_KRAS <- read.csv("filtered_cosmic_hits_KRAS.csv", header = T)
filtered_cosmic_hits_P53 <- read.csv("filtered_cosmic_hits_P53.csv", header = T)
filtered_cosmic_hits_STK11 <- read.csv("filtered_cosmic_hits_STK11.csv", header = T)
```

get cell names and get rid of underscores
```{r}
BRAF_cells0 <- filtered_cosmic_hits_BRAF$cellName
BRAF_cells <- gsub("_", ".", BRAF_cells0)

EGFR_cells0 <- filtered_cosmic_hits_EGFR$cellName
EGFR_cells <- gsub("_", ".", EGFR_cells0)

KRAS_cells0 <- filtered_cosmic_hits_KRAS$cellName
KRAS_cells <- gsub("_", ".", KRAS_cells0)

P53_cells0 <- filtered_cosmic_hits_P53$cellName
P53_cells <- gsub("_", ".", P53_cells0)

STK11_cells0 <- filtered_cosmic_hits_STK11$cellName
STK11_cells <- gsub("_", ".", STK11_cells0)
```

get ALK fus cells from STAR-fus
```{r}
alkFusCells <- c('C10.B003527', 'C15.B003527', 'I13.1001000369', 'J17.B003527', 'K11.B003588', 'M11.B003588', 'N14.B003588', 'O9.B000861')
```

get cells contained in multiple lists?
```{r}
i1 <- intersect(BRAF_cells, EGFR_cells)
```

concat
```{r}
allCells_w_driver_muts <- c(BRAF_cells, EGFR_cells, KRAS_cells, P53_cells, STK11_cells, alkFusCells)
```

set everything to grey
```{r}
# copy this guy
justMalig1 <- justMalig

for(i in 1:nrow(justMalig1@meta.data)){
  justMalig1@ident[i] <- NA
}
```

get indicies
```{r}
BRAF_indicies <- which(row.names(justMalig1@meta.data) %in% BRAF_cells)
EGFR_indicies <- which(row.names(justMalig1@meta.data) %in% EGFR_cells)
KRAS_indicies <- which(row.names(justMalig1@meta.data) %in% KRAS_cells)
P53_indicies <- which(row.names(justMalig1@meta.data) %in% P53_cells)
STK11_indicies <- which(row.names(justMalig1@meta.data) %in% STK11_cells)
ALK_indicies <- which(row.names(justMalig1@meta.data) %in% alkFusCells)
```

reset idents 
```{r}
justMalig1@ident[BRAF_indicies] <- 1
justMalig1@ident[EGFR_indicies] <- 2
justMalig1@ident[KRAS_indicies] <- 3
justMalig1@ident[P53_indicies] <- 4
justMalig1@ident[STK11_indicies] <- 5
justMalig1@ident[ALK_indicies] <- 6
```

plot again
```{r}
TSNEPlot(object = justMalig, do.label = T)
pdf("justMalig1.pdf", 10, 10)
TSNEPlot(object = justMalig1, do.label = F, pt.size = 2)
dev.off()
```

can we make a barplot? 
```{r}
unique(justMalig@ident) # 15 clusters

c0_indices <- which(justMalig@ident == 0)
c0_cells <- row.names(justMalig@meta.data)[c0_indices]

c1_indices <- which(justMalig@ident == 1)
c1_cells <- row.names(justMalig@meta.data)[c1_indices]

c2_indices <- which(justMalig@ident == 2)
c2_cells <- row.names(justMalig@meta.data)[c2_indices]

c3_indices <- which(justMalig@ident == 3)
c3_cells <- row.names(justMalig@meta.data)[c3_indices]

c4_indices <- which(justMalig@ident == 4)
c4_cells <- row.names(justMalig@meta.data)[c4_indices]

c5_indices <- which(justMalig@ident == 5)
c5_cells <- row.names(justMalig@meta.data)[c5_indices]

c6_indices <- which(justMalig@ident == 6)
c6_cells <- row.names(justMalig@meta.data)[c6_indices]

c7_indices <- which(justMalig@ident == 7)
c7_cells <- row.names(justMalig@meta.data)[c7_indices]

c8_indices <- which(justMalig@ident == 8)
c8_cells <- row.names(justMalig@meta.data)[c8_indices]

c9_indices <- which(justMalig@ident == 9)
c9_cells <- row.names(justMalig@meta.data)[c9_indices]

c10_indices <- which(justMalig@ident == 10)
c10_cells <- row.names(justMalig@meta.data)[c10_indices]

c11_indices <- which(justMalig@ident == 11)
c11_cells <- row.names(justMalig@meta.data)[c11_indices]
```

get matches
```{r}
c0_matches <- which(c0_cells %in% allCells_w_driver_muts)
c1_matches <- which(c1_cells %in% allCells_w_driver_muts)
c2_matches <- which(c2_cells %in% allCells_w_driver_muts)
c3_matches <- which(c3_cells %in% allCells_w_driver_muts)
c4_matches <- which(c4_cells %in% allCells_w_driver_muts)
c5_matches <- which(c5_cells %in% allCells_w_driver_muts)
c6_matches <- which(c6_cells %in% allCells_w_driver_muts)
c7_matches <- which(c7_cells %in% allCells_w_driver_muts)
c8_matches <- which(c8_cells %in% allCells_w_driver_muts)
c9_matches <- which(c9_cells %in% allCells_w_driver_muts)
c10_matches <- which(c10_cells %in% allCells_w_driver_muts)
c11_matches <- which(c11_cells %in% allCells_w_driver_muts)
```

get lengths
```{r}
length(c0_matches)
length(c1_matches)
length(c2_matches)
length(c3_matches)
length(c4_matches)
length(c5_matches)
length(c6_matches)
length(c7_matches)
length(c8_matches)
length(c9_matches)
length(c10_matches)
length(c11_matches)
```

convert this guy into a df
```{r}
matches_df <- c(length(c0_matches), length(c1_matches), length(c2_matches), length(c3_matches), length(c4_matches), length(c5_matches), length(c6_matches), length(c7_matches), length(c8_matches), length(c9_matches), length(c10_matches), length(c11_matches))

matches_df <- as.data.frame(matches_df)
colnames(matches_df) <- "count"
matches_df$cluster <- NA
matches_df$cluster <- c(0,1,2,3,4,5,6,7,8,9,10,11)
```

add a col -- number of cells / cluster
```{r}
matches_df$clusterSize <- NA

matches_df$clusterSize[1] <- length(c0_cells)
matches_df$clusterSize[2] <- length(c1_cells)
matches_df$clusterSize[3] <- length(c2_cells)
matches_df$clusterSize[4] <- length(c3_cells)
matches_df$clusterSize[5] <- length(c4_cells)
matches_df$clusterSize[6] <- length(c5_cells)
matches_df$clusterSize[7] <- length(c6_cells)
matches_df$clusterSize[8] <- length(c7_cells)
matches_df$clusterSize[9] <- length(c8_cells)
matches_df$clusterSize[10] <- length(c9_cells)
matches_df$clusterSize[11] <- length(c10_cells)
matches_df$clusterSize[12] <- length(c11_cells)
```

need to normalize to number of cells per cluster
```{r}
matches_df$normcount <- NA

matches_df$normcount[1] <- matches_df$count[1] / matches_df$clusterSize[1]
matches_df$normcount[2] <- matches_df$count[2] / matches_df$clusterSize[2]
matches_df$normcount[3] <- matches_df$count[3] / matches_df$clusterSize[3]
matches_df$normcount[4] <- matches_df$count[4] / matches_df$clusterSize[4]
matches_df$normcount[5] <- matches_df$count[5] / matches_df$clusterSize[5]
matches_df$normcount[6] <- matches_df$count[6] / matches_df$clusterSize[6]
matches_df$normcount[7] <- matches_df$count[7] / matches_df$clusterSize[7]
matches_df$normcount[8] <- matches_df$count[8] / matches_df$clusterSize[8]
matches_df$normcount[9] <- matches_df$count[9] / matches_df$clusterSize[9]
matches_df$normcount[10] <- matches_df$count[10] / matches_df$clusterSize[10]
matches_df$normcount[11] <- matches_df$count[11] / matches_df$clusterSize[11]
matches_df$normcount[12] <- matches_df$count[12] / matches_df$clusterSize[12]
```

get ave coverage per cluster
```{r}
nReads_c0 <- ave(justMalig@meta.data$nReads[c0_indices])
nReads_c1 <- ave(justMalig@meta.data$nReads[c1_indices])
nReads_c2 <- ave(justMalig@meta.data$nReads[c2_indices])
nReads_c3 <- ave(justMalig@meta.data$nReads[c3_indices])
nReads_c4 <- ave(justMalig@meta.data$nReads[c4_indices])
nReads_c5 <- ave(justMalig@meta.data$nReads[c5_indices])
nReads_c6 <- ave(justMalig@meta.data$nReads[c6_indices])
nReads_c7 <- ave(justMalig@meta.data$nReads[c7_indices])
nReads_c8 <- ave(justMalig@meta.data$nReads[c8_indices])
nReads_c9 <- ave(justMalig@meta.data$nReads[c9_indices])
nReads_c10 <- ave(justMalig@meta.data$nReads[c10_indices])
nReads_c11 <- ave(justMalig@meta.data$nReads[c11_indices])
```

add col to matches_df
```{r}
matches_df$nReads <- NA

matches_df$nReads[1] <- nReads_c0
matches_df$nReads[2] <- nReads_c1
matches_df$nReads[3] <- nReads_c2
matches_df$nReads[4] <- nReads_c3
matches_df$nReads[5] <- nReads_c4
matches_df$nReads[6] <- nReads_c5
matches_df$nReads[7] <- nReads_c6
matches_df$nReads[8] <- nReads_c7
matches_df$nReads[9] <- nReads_c8
matches_df$nReads[10] <- nReads_c9
matches_df$nReads[11] <- nReads_c10
matches_df$nReads[12] <- nReads_c11
```

```{r}
matches_df$normcount_perKilobase <- NA

matches_df$normcount_perKilobase[1] <- matches_df$normcount[1] / (matches_df$nReads[1] / 1000)
matches_df$normcount_perKilobase[2] <- matches_df$normcount[2] / (matches_df$nReads[2] / 1000)
matches_df$normcount_perKilobase[3] <- matches_df$normcount[3] / (matches_df$nReads[3] / 1000)
matches_df$normcount_perKilobase[4] <- matches_df$normcount[4] / (matches_df$nReads[4] / 1000)
matches_df$normcount_perKilobase[5] <- matches_df$normcount[5] / (matches_df$nReads[5] / 1000)
matches_df$normcount_perKilobase[6] <- matches_df$normcount[6] / (matches_df$nReads[6] / 1000)
matches_df$normcount_perKilobase[7] <- matches_df$normcount[7] / (matches_df$nReads[7] / 1000)
matches_df$normcount_perKilobase[8] <- matches_df$normcount[8] / (matches_df$nReads[8] / 1000)
matches_df$normcount_perKilobase[9] <- matches_df$normcount[9] / (matches_df$nReads[9] / 1000)
matches_df$normcount_perKilobase[10] <- matches_df$normcount[10] / (matches_df$nReads[10] / 1000)
matches_df$normcount_perKilobase[11] <- matches_df$normcount[11] / (matches_df$nReads[11] / 1000)
matches_df$normcount_perKilobase[12] <- matches_df$normcount[12] / (matches_df$nReads[12] / 1000)
```

plot
```{r}
#pdf("matches_df.pdf", 10, 10)
p <- ggplot(matches_df, aes(cluster, y=normcount))
p + geom_bar(stat = "identity") + xlab("cluster") + ylab("Driver mutations per cell") + scale_x_continuous(breaks = round(seq(min(matches_df$cluster), max(matches_df$cluster), by = 1)))
#dev.off()

p1 <- ggplot(matches_df, aes(cluster, y=normcount_perKilobase))
p1 + geom_bar(stat = "identity") + xlab("cluster") + ylab("Driver mutations per cell per kilobase") + scale_x_continuous(breaks = round(seq(min(matches_df$cluster), max(matches_df$cluster), by = 1)))
```

///////////////////////////////////////////////////////////////////////////////
///////////////////////////////////////////////////////////////////////////////
///////////////////////////////////////////////////////////////////////////////
ZOOM IN ON C4? 

set this back 
```{r}
c4_cells <- gsub("[.]", "_", c4_cells)
```

get hit cells w/in c4
```{r}
c4_indicies_toKeep <- which(filtered_cosmic_hits_BRAF$cellName %in% c4_cells)
c4_indicies_toKeep1 <- which(filtered_cosmic_hits_EGFR$cellName %in% c4_cells)
c4_indicies_toKeep2 <- which(filtered_cosmic_hits_KRAS$cellName %in% c4_cells)
c4_indicies_toKeep3 <- which(filtered_cosmic_hits_P53$cellName %in% c4_cells)
c4_indicies_toKeep4 <- which(filtered_cosmic_hits_STK11$cellName %in% c4_cells)

filtered_cosmic_hits_BRAF_c4 <- filtered_cosmic_hits_BRAF[c4_indicies_toKeep,]
filtered_cosmic_hits_EGFR_c4 <- filtered_cosmic_hits_EGFR[c4_indicies_toKeep1,]
filtered_cosmic_hits_KRAS_c4 <- filtered_cosmic_hits_KRAS[c4_indicies_toKeep2,]
filtered_cosmic_hits_P53_c4 <- filtered_cosmic_hits_P53[c4_indicies_toKeep3,]
filtered_cosmic_hits_STK11_c4 <- filtered_cosmic_hits_STK11[c4_indicies_toKeep4,]
```

get Alk/Eml4 fus
```{r}
# none
which(alkFusCells %in% c4_cells)
```

number of unique mutations found
```{r}
length(unique(filtered_cosmic_hits_BRAF_c4$Mutation.genome.position))
length(unique(filtered_cosmic_hits_EGFR_c4$Mutation.genome.position))
length(unique(filtered_cosmic_hits_KRAS_c4$Mutation.genome.position))
length(unique(filtered_cosmic_hits_P53_c4$Mutation.genome.position))
length(unique(filtered_cosmic_hits_STK11_c4$Mutation.genome.position))
```

across how many cells? 
```{r}
length(unique(filtered_cosmic_hits_BRAF_c4$cellName))
length(unique(filtered_cosmic_hits_EGFR_c4$cellName))
length(unique(filtered_cosmic_hits_KRAS_c4$cellName))
length(unique(filtered_cosmic_hits_P53_c4$cellName))
length(unique(filtered_cosmic_hits_STK11_c4$cellName))
```

///////////////////////////////////////////////////////////////////////////////
///////////////////////////////////////////////////////////////////////////////
///////////////////////////////////////////////////////////////////////////////

NOW LETS LOOK AT C7

set this back 
```{r}
c7_cells <- gsub("[.]", "_", c7_cells)
```

get hit cells w/in c7
```{r}
c7_indicies_toKeep <- which(filtered_cosmic_hits_BRAF$cellName %in% c7_cells)
c7_indicies_toKeep1 <- which(filtered_cosmic_hits_EGFR$cellName %in% c7_cells)
c7_indicies_toKeep2 <- which(filtered_cosmic_hits_KRAS$cellName %in% c7_cells)
c7_indicies_toKeep3 <- which(filtered_cosmic_hits_P53$cellName %in% c7_cells)
c7_indicies_toKeep4 <- which(filtered_cosmic_hits_STK11$cellName %in% c7_cells)

filtered_cosmic_hits_BRAF_c7 <- filtered_cosmic_hits_BRAF[c7_indicies_toKeep,]
filtered_cosmic_hits_EGFR_c7 <- filtered_cosmic_hits_EGFR[c7_indicies_toKeep1,]
filtered_cosmic_hits_KRAS_c7 <- filtered_cosmic_hits_KRAS[c7_indicies_toKeep2,]
filtered_cosmic_hits_P53_c7 <- filtered_cosmic_hits_P53[c7_indicies_toKeep3,]
filtered_cosmic_hits_STK11_c7 <- filtered_cosmic_hits_STK11[c7_indicies_toKeep4,]
```

get Alk/Eml4 fus
```{r}
which(alkFusCells %in% c7_cells)
```

number of unique mutations found
```{r}
length(unique(filtered_cosmic_hits_BRAF_c7$Mutation.genome.position))
length(unique(filtered_cosmic_hits_EGFR_c7$Mutation.genome.position))
length(unique(filtered_cosmic_hits_KRAS_c7$Mutation.genome.position))
length(unique(filtered_cosmic_hits_P53_c7$Mutation.genome.position))
length(unique(filtered_cosmic_hits_STK11_c7$Mutation.genome.position))
```

across how many cells? 
```{r}
length(unique(filtered_cosmic_hits_BRAF_c7$cellName))
length(unique(filtered_cosmic_hits_EGFR_c7$cellName))
length(unique(filtered_cosmic_hits_KRAS_c7$cellName))
length(unique(filtered_cosmic_hits_P53_c7$cellName))
length(unique(filtered_cosmic_hits_STK11_c7$cellName))
```
